Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-23 draft.tex
Added index terms.

\begin{keywords}
\vskip-\baselineskip
\end{keywords}

@@

\note{What is $w$ here?}

@@

\note{I did't like this passage. It made it seem obvious that the nonlinearities are contained in a polytope spanned by
extremal values.. That's obviously not the case.. [We can assume this
if $f$ is continuously differentiable]}

@@

expressions defining $(H^x_k,H^u_k)$ pointwise. For this we use the numerical values for the example of the 

@@

For this example the greatest sensitivity corresponds to $\alpha_3$ with a numerical value of $2.6458\times 10^9$, 

@@

\note{I actually have no idea what the numerical value means. It sort of tells us that at least one constraint depending on $\alpha_3$
is highly sensitive. The actual numerical value could also imply that it is a constraint on $\alpha_3$ which has some residual dependence on
$\alpha_3$ and is blown up by normalising. [some comment is needed in
the text]}

>>>>

\begin{keywords}
constrained control, positively invariant sets, robust control
\vskip-\baselineskip
\end{keywords}

@@

@@

@@

expressions defining $(H^x_k,H^u_k)$ pointwise.
This leads to an inner approximation of the linearisation error set, however we can make it as tight as necessary
by increasing the number of samples.
For this we use the numerical values for the example of the 

@@

For this example the greatest sensitivity corresponds to $\alpha_3$, 

@@
